The problem and promise of scale in multilayer networks

### 2019-12-08 paper/introduction.Rmd
more skeleton

<!-- Landscape spatial scale -->
<!-- Social proximity scale -->
<!-- Regular networks -->
<!-- Multilayer networks -->
<!-- Case study -->

>>>>

<!-- Landscape spatial scale -->

<!-- Social proximity scale -->

<!-- Regular networks
* SNA significant outcomes
-->

<!-- Multilayer networks
used across disciplines
-->
Multilayer networks explicitly consider social systems across temporal, spatial and social contexts [@pilosof2017a]. They are made up of multiple layers, each representing relationships, individuals, spatial areas or temporal windows [@kivela2014; @porter2018a]. Recently used in animal behaviour studies, multilayer networks have the potential to better characterize complex social systems [@silk2018a; @finn2019].

<!-- Case study 
deer
fogo caribou
-->
